Inferring neural networks from fluorescent calcium imaging using partial correlation and sample weighting

### 2014-06-06 article.tex
rework strucutre + add reference for datasets
Add dataset description

% Solution
In this paper, we describe a simple and a theoretically grounded approach
based on partial correlation to infer the neural connectivity network.
This is also the winning method of the Connectomics challenge
\footnote{\url{http://connectomics.chalearn.org/}}.

\section{Signal filtering methodology}
\label{sec:filter}
% Explain why we need to filter
% TODO

@@

\section{Network inference methodology}
\label{sec:inference}

@@

\section{Stacking methodology}
\label{sec:stacking}

@@

\section{Causal discovery methodology}
% Introduce a custom solution to make the Y matrix asymmetric
% Introduce directivity
Since the partial correlation is a symmetric measure, the causal mechanism behind the
interaction ($A$ directly causes $B$, $B$ directly causes $A$ or both) can not
be inferred\footnote{Also note that two other causal mechanisms might be
implied while having a non-zero partial coefficient: (i) a pair of variables
is induced by a common (hidden) variable; (ii) $A$ (respectively $B$) is
conditionally correlated to a hidden variable affecting $B$ (resp. $A$)
\cite{de2004discovery}.} directly from a symmetric adjacency matrix.

@@

\section{Empirical experiments}
\subsection{Datasets}

\subsection{Metrics}
\subsection{Data filtering}
\subsection{Signal distribution}
\subsection{ROC AUC results}
\paragraph{Improvement of each stage of our approach\\}

@@

\begin{table}[htb]
\centering
\begin{tabular}{|c|c||c|c|c|c|} \hline
\# & Stage & normal-1 & normal-2 & normal-3 & normal-4 \\ \hline
1 & Inverse correlation & & & &\\ \hline
2 & Correlation & & & &\\ \hline
3 & GENIE3 & & & & \\ \hline
4 & GTE & & & & \\ \hline

\end{tabular}
\end{table}
\subsection{Discussion about the metric}
\label{sec:metric}

@@

% Possible extensions
% partial autocorrelation function (sometimes "partial correlation function")
% conditional independence test

>>>>

% Solution
In this paper, we describe a simple and a theoretically grounded approach
based on partial correlation to infer the neural connectivity network.
This is also the winning method of the Connectomics challenge
\footnote{\url{http://connectomics.chalearn.org/}}. For reproducibility, the
source code of the method is available at
\url{https://github.com/asutera/kaggle-connectomics} under 3-clause BSD
license.

\section{Methodology}
\section{Signal filtering} \label{sec:filter}
% Explain why we need to filter
% TODO

@@

\subsection{Network inference through partial correlation}
\label{sec:inference}

@@

\subsection{Stacking partial correlation matrix}
\label{sec:stacking}

@@

\subsection{Causal discovery methodology}
% Introduce a custom solution to make the Y matrix asymmetric
% Introduce directivity
Since the partial correlation is a symmetric measure, the causal mechanism behind the
interaction ($A$ directly causes $B$, $B$ directly causes $A$ or both) can not
be inferred\footnote{Also note that two other causal mechanisms might be
implied while having a non-zero partial coefficient: (i) a pair of variables
is induced by a common (hidden) variable; (ii) $A$ (respectively $B$) is
conditionally correlated to a hidden variable affecting $B$ (resp. $A$)
\cite{de2004discovery}.} directly from a symmetric adjacency matrix.

@@

\section{Experiments}
\subsection{Accuracy assessment protocol}
% Datasets
To assess our method, we have used four datasets provided by the organizer
of the Connectomics challenge : normal-1, normal-2, normal-3, normal-4. Those
datasets are time series of size $n=179500$ of image calcium from simulated
neuronal network \cite{stetter2012model} with $p=1000$ neurons. The networks
to inferred have around 15000 arcs or a density of $0.15\%$.

% Metrics : ROC AUC an AUPRC
% We assess the accuracy of the neuronal network

\subsection{Data filtering and Signal distribution}

\subsection{Inference of neuronal network}

\paragraph{Improvement of each stage of our approach\\}

@@

\begin{table}[htb]
\centering
\begin{tabular}{|c|c||c|c|c|c|} \hline
\# & Stage & normal-1 & normal-2 & normal-3 & normal-4 \\ \hline
1 & Inverse correlation & & & &\\ \hline
2 & Correlation & & & &\\ \hline
3 & GENIE3 & & & & \\ \hline
4 & GTE & & & & \\ \hline
\end{tabular}
\end{table}
\subsection{Discussion about the metric}
\label{sec:metric}

@@

% Possible extensions
% partial autocorrelation function (sometimes "partial correlation function")
% conditional independence test
% Speak about the complexity and parallelization of the methods
